BivData Setup

### 2020-02-11 src/BivData_Setup.Rmd
fixed a bug for a strain level table

                       mean.SC_length = mean(chromosomeLength, na.rm = TRUE),
                       var.SC_length = var(chromosomeLength, na.rm = TRUE),
                       sd.SC_length   = round(sd(chromosomeLength), 3),
                       se.SC_length   = round(sd.SC_length / sqrt(nbivs), 3),

@@

as.data.frame( head(mouse.level.BivData_table) )
#kable didn't work

@@

#is there a way that the above table would be different than the 
Mouse.Table_BivData_4MM <- ddply(Curated_BivData, c("mouse"), summarise,
                        Nmice = length(unique(mouse)),
                        Ncells  = length(  unique(fileName) ),
                      tot.biv = length(Obj.ID),

@@

              mean.telo.dist = mean(telo_dist, na.rm=TRUE),
              mean.cent.dist = mean(dis.cent, na.rm=TRUE)
)
Mouse.Table_BivData_4MM <- Mouse.Table_BivData_4MM[(!is.na(Mouse.Table_BivData_4MM$mouse)),]

@@

#remove all the non-used strains!!
Mouse.Table_BivData_4MM <- Mouse.Table_BivData_4MM[Mouse.Table_BivData_4MM$strain != "AST",]
Mouse.Table_BivData_4MM <- Mouse.Table_BivData_4MM[Curated_BivData$strain != "TOM",]
Mouse.Table_BivData_4MM <- Mouse.Table_BivData_4MM[Mouse.Table_BivData_4MM$strain != "CZECH",]
Mouse.Table_BivData_4MM$strain <- droplevels(Mouse.Table_BivData_4MM$strain)

#assign high and low
#divide musc males into groups
#mouse.avs_4MM$Rec.group.alt <- ifelse(grepl("PWD male", mouse.avs_4MM$category), 1, 
#                                ifelse(grepl("MSM male", mouse.avs_4MM$category), 1,
#                                 ifelse(grepl("SKIVE male", mouse.avs_4MM$category), 1, 0)))#
#
#mouse.avs_4MM$Rec.group <- ifelse(grepl("PWD male", mouse.avs_4MM$category), 1, 
#                                ifelse(grepl("MSM male", mouse.avs_4MM$category), 1, 0))
```

@@

#save Rdata
save.image("~./MLH1repo/data/CleanBivData_3.2.20.RData")
#save.image("data/BivData_4_PCA.RData")

>>>>

                       Nbiv = length(Obj.ID), #if there are na's below -- it breaks
                       tot.biv = length(Obj.ID),

                       n0CO = sum( (hand.foci.count == 0), na.rm = TRUE ),
                      n1CO = sum( (hand.foci.count == 1), na.rm = TRUE ),
                      n2CO = sum( (hand.foci.count == 2), na.rm = TRUE ),
                      n3CO = sum( (hand.foci.count == 3), na.rm = TRUE ),
                      n4CO = sum(hand.foci.count == 4, na.rm=TRUE),

                       mean.SC_length = mean(chromosomeLength, na.rm = TRUE),
                       var.SC_length = var(chromosomeLength, na.rm = TRUE),
                       sd.SC_length   = round(sd(chromosomeLength), 3),
                       se.SC_length   = round(sd.SC_length / sqrt(Nbiv), 3),

@@

mouse.level.BivData_table <- add_sex(mouse.level.BivData_table)
mouse.level.BivData_table <- add_strain(mouse.level.BivData_table)
mouse.level.BivData_table <- add_subsp(mouse.level.BivData_table)
mouse.level.BivData_table <- add_category(mouse.level.BivData_table)

#unordered for the mixed models (move this to the MM blocks...?)
mouse.level.BivData_table$subsp <- factor(mouse.level.BivData_table$subsp, ordered = FALSE)
mouse.level.BivData_table$sex <- factor(mouse.level.BivData_table$sex, ordered = FALSE)
mouse.level.BivData_table$strain <- factor(mouse.level.BivData_table$strain, ordered = FALSE)

@@

Mouse.Table_BivData_4MM <- ddply(Curated_BivData, c("mouse"), summarise,
                        Nmice = length(unique(mouse)),
                        Ncells  = length(  unique(fileName) ),
                      tot.biv = length(Obj.ID),

@@

@@

#remove all the non-used strains!!

Mouse.Table_BivData_4MM <-  Mouse.Table_BivData_4MM %>%  filter(strain != "AST")  %>% filter(strain != "TOM")  %>% filter(strain != "CZECH")

#Mouse.Table_BivData_4MM$strain <- droplevels(Mouse.Table_BivData_4MM$strain)
#Mouse.Table_BivData_4MM <- Mouse.Table_BivData_4MM[(!is.na(Mouse.Table_BivData_4MM$mouse)),] #so many NAs still

Mouse.Table_BivData_4MM$Rec.group <- ifelse(grepl("PWD male", Mouse.Table_BivData_4MM$category), 1, 
                              ifelse(grepl("MSM male", Mouse.Table_BivData_4MM$category), 1,
                                 ifelse(grepl("SKIVE male", Mouse.Table_BivData_4MM$category), 1, 0)))

@@

#save Rdata
save.image("~./MLH1repo/data/CleanBivData_11.2.20.RData")
#save.image("data/BivData_4_PCA.RData")
